SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-04-17 Chapters/Chapter02.tex
papers TODO

    But it feels like a mistake to say that that is thinking.  It's not.  It is to me a great model of someone getting so attuned into an area that they are able to simply flow through tasks; in the positive psychology sense of the word flow.  It's very powerful and very intelligent:  but it is a form of intelligence without thinking.  Intelligence that can't make leaps from one arena to another; Intelligence that can't work on Bongard problems.  So what I would fear as a dead-end in research would be to have another AI winter... decades of massive, massive number-crunching and machine learning of this type... in disregard to big questions such as the interaction of short-term memory with SDM and, again, tasks like Bongard problems (Figure \ref{fig:bongard-problems-71}).  Bongard problems demand high-gossip between system 1 and system 2; they demand a high dose of imagination and mental imagery manipulation; they demand discrimination and demand clusterization, among many other things that have been spelled out before by \citet{bongard_recognition_1968, douglas1980godel, Linhares2000, foundalis_phaeaco:_2006, lupyan_difficulties_2013} and others.

>>>>

    But it feels like a mistake to say that that is thinking.  It's not.  It is to me a great model of someone getting so attuned into an area that they are able to simply flow through tasks; in the positive psychology sense of the word flow.  It's very powerful and very intelligent:  but it is a form of intelligence without thinking.  Intelligence that can't make leaps from one arena to another; Intelligence that can't work on Bongard problems.  So what I would fear as a dead-end in research would be to have another AI winter... decades of massive, massive number-crunching and machine learning of this type... in disregard to big questions such as the interaction of short-term memory with SDM and, again, tasks like Bongard problems (Figure \ref{fig:bongard-problems-71}).  Bongard problems demand high-gossip between system 1 and system 2; they demand a high dose of imagination and mental imagery manipulation; they demand discrimination and demand clusterization, among many other things that have been spelled out before by \citet{bongard_recognition_1968, douglas1980godel, Linhares2000} and the only serious, deep, study being citet{foundalis_phaeaco:_2006}.

### 2018-04-17 Chapters/Chapter0A.tex
papers TODO

Finally, how long does it take for a dissertation to be completed? The time is either less than or equal to the duration allowed by the Grad College for the completion of a Ph.D or it is greater. In the latter case, infinite number of petitions can be filed for extensions. Since the Grad College never remembers previous petitions, the total number of petitions received by the Grad College is always one, a small constant\footnote{`With apologies to non-CS types': this wonderful result is from Bala Rajagopalan, posted on the late rec.humor.funny Usenet in June 12 1989.}.

>>>>

Finally, how long does it take for a dissertation to be completed? The time is either less than or equal to the duration allowed by the Grad College for the completion of a Ph.D or it is greater. In the latter case, infinite number of petitions can be filed for extensions. Since the Grad College never remembers previous petitions, the total number of petitions received by the Grad College is always one, a small constant\footnote{`With apologies to non-CS types': this seminal, wonderful, result is from Bala Rajagopalan, published on the late rec.humor.funny Usenet in June 12, 1989.  Thank you for reading my thesis!}.
